Funding programmes for early career researchers do/not influence their independence

### 2023-07-25 _targets.Rmd
new data pipeline for matching + updated parts of database

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs",
                            "tidyverse",
                            "psych",
                            "arrow",
                            "tarchetypes"
                            ))

@@

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow")),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow")),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_supervisors_control"),
      paths = here::here("data", "raw", "supervisors_control_final.csv")),

     # tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(db_path, here::here("data", "raw", "czech_sci_db.sqlite")),
     # tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     # tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(ids_complete, create_ids_complete(ids, db_path)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete))

@@

      tar_target(matching, match(db_path, ids, gender, authors_arrow)),
      # tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs",
                            "tidyverse",
                            "psych",
                            "arrow",
                            "tarchetypes",
                            "cobalt"
                            ))

@@

  tarchetypes::tar_download(ids_path,
      urls = Sys.getenv("link_to_supervisors"),
      paths = here::here("data", "raw", "supervisors.csv")),
  tarchetypes::tar_download(gender_path,
      urls = Sys.getenv("link_to_gender"),
      paths = here::here("data", "raw", "names4api_tagged.tsv")),
  tarchetypes::tar_download(authors_arrow_path,
      urls = Sys.getenv("link_to_updated_authors"),
      paths = here::here("data", "raw", "authors_by_pubs.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(text_arrow_path,
      urls = Sys.getenv("link_to_updated_texts"),
      paths = here::here("data", "raw", "riv_text.arrow"),
      mode = "wb"),
  tarchetypes::tar_download(cep_investigators_path,
      urls = Sys.getenv("link_to_cep_investigators"),
      paths = here::here("data", "raw", "cep_investigators.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(cep_details_path,
      urls = Sys.getenv("link_to_cep_details"),
      paths = here::here("data", "raw", "cep_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_details_path,
      urls = Sys.getenv("link_to_riv_details"),
      paths = here::here("data", "raw", "riv_details.arrow"),
       mode = "wb"),
  tarchetypes::tar_download(riv_authors_path,
      urls = Sys.getenv("link_to_riv_authors"),
      paths = here::here("data", "raw", "riv_authors.arrow"),
       mode = "wb"),
   tarchetypes::tar_download(sup_path,
      urls = Sys.getenv("link_to_supervisors_control"),
      paths = here::here("data", "raw", "supervisors_control_final.csv")),

     # tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(db_path, here::here("data", "raw", "czech_sci_db.sqlite")),
     # tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     # tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(cep_investigators_arrow, arrow::read_feather(cep_investigators_path)),
     tar_target(cep_details_arrow, arrow::read_feather(cep_details_path)),
     tar_target(riv_details_arrow, arrow::read_feather(riv_details_path)),
     tar_target(riv_authors_arrow, arrow::read_feather(riv_authors_path)),
     tar_target(ids_complete, create_ids_complete(ids, db_path)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete))

@@

      tar_target(matching_data, match_data_prep(db_path, ids, gender, authors_arrow, cep_investigators_arrow, cep_details_arrow, riv_details_arrow, riv_authors_arrow)),
      tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 
      tar_target(matched_obj_funded, match_obj_funded(db_path, authors_arrow, matching_data)),
      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded)),
      # tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

### 2023-07-25 article.Rmd
new data pipeline for matching + updated parts of database

---
title: "Funding programmes for early career researchers do/not influence their independence"
author: "David Janků"
output: html_document
---

@@

Although researcher independence seems to be important feature that is acknowledged by many actors in the research systems and that research funders try to stimulate, there hasn’t been much effort focused on quantifying this phenomenon. Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g. Rojko & Lužar, 2022). However, such indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether given researcher become independent in their thinking and research topics. Van den Besselaar & Sandström (2019) therefore proposed more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps. Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of it’s impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021).

@@

```{r echo=FALSE}
# Create a subset for treatment group and control group 1
subset_1 <- (tar_read(matching)) %>% filter(treatment != 2)
subset_2 <- (tar_read(matching)) %>% filter(treatment != 0)

# Generate balance table for treatment vs control group 1
balance_results_1 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_1, disp = c("mean", "std"))
balance_results_2 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_2, disp = c("mean", "std"))

# Define a function to manually extract balance statistics from bal.tab object
extract_balance_stats <- function(bal_results) {
  covariates <- rownames(bal_results$Balance)
  means_treat <- bal_results$Balance$`M.1.Un`
  means_ctrl <- bal_results$Balance$`M.0.Un`
  diff <- bal_results$Balance$`Diff.Un`

  data.frame(Covariate = covariates, 
             Mean_Treatment = means_treat, 
             Mean_Control = means_ctrl, 
             Diff = diff)
}

# Extract balance stats for subset_1 and subset_2
balance_stats_1 <- extract_balance_stats(balance_results_1)
balance_stats_2 <- extract_balance_stats(balance_results_2)

# Print tables in R Markdown
knitr::kable(balance_stats_1, caption = "Balance Statistics: Treatment vs Control Group 1") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
knitr::kable(balance_stats_2, caption = "Balance Statistics: Treatment vs Control Group 2") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

>>>>

---
title: "Funding programmes for early career researchers do/not influence their independence"
author: "David Janků"
date: "`r Sys.Date()`"
output: html_document
bibliography: researcher_independence.bib
csl: apa.csl
---

@@

Although researcher independence seems to be important feature that is acknowledged by many actors in the research systems and that research funders try to stimulate, there hasn’t been much effort focused on quantifying this phenomenon. Some studies try to measure independence in a simple way, as a ratio of publications the given researcher produced without their supervisor divided by the total number of publications of the given researchers (e.g. Rojko & Lužar, 2022). However, such indicator could be misleading in the world of team science, and also only focuses on collaborations, not tracking whether given researcher become independent in their thinking and research topics. [@vandenbesselaarMeasuringResearcherIndependence2019] therefore proposed more complex indicator for measuring researcher independence on the individual level, based on co-authorship network and topical overlaps. Their measure uses only information about publications’ characteristics (authorship and reference list) regardless of it’s impacts, unlike other alternative measures that focus solely on the impact of the independent work in terms of received citations (Dey, et al., 2021).

@@

```{r echo=FALSE}
# # Create a subset for treatment group and control group 1
# subset_1 <- (tar_read(matching)) %>% filter(treatment != 2)
# subset_2 <- (tar_read(matching)) %>% filter(treatment != 0)
# 
# # Generate balance table for treatment vs control group 1
# balance_results_1 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_1, disp = c("mean", "std"))
# balance_results_2 <- bal.tab(treatment ~ career_lenght + pubs_total + ws_pubs + interdisc_proportion + grants + gender, data = subset_2, disp = c("mean", "std"))
# 
# # Define a function to manually extract balance statistics from bal.tab object
# extract_balance_stats <- function(bal_results) {
#   covariates <- rownames(bal_results$Balance)
#   means_treat <- bal_results$Balance$`M.1.Un`
#   means_ctrl <- bal_results$Balance$`M.0.Un`
#   diff <- bal_results$Balance$`Diff.Un`
#   
#   data.frame(Covariate = covariates, 
#              Mean_Treatment = means_treat, 
#              Mean_Control = means_ctrl, 
#              Diff = diff)
# }
# 
# # Extract balance stats for subset_1 and subset_2
# balance_stats_1 <- extract_balance_stats(balance_results_1)
# balance_stats_2 <- extract_balance_stats(balance_results_2)
# 
# # Print tables in R Markdown
# knitr::kable(balance_stats_1, caption = "Balance Statistics: Treatment vs Control Group 1") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
# knitr::kable(balance_stats_2, caption = "Balance Statistics: Treatment vs Control Group 2") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

unf_sum <- summary(matched_obj_unfunded, un = FALSE)

summary(matched_obj_unfunded)

plot(unf_sum, var.order = "unmatched")

cobalt::bal.tab(matched_obj_unfunded, un = FALSE, stats = c("m", "v", "ks"), binary = "std")

cobalt::love.plot(matched_obj_unfunded, binary = "std", var.order = "unmatched")

fun_sum <- summary(matched_obj_funded, un = FALSE)

summary(matched_obj_funded)

plot(fun_sum, var.order = "unmatched")

@@

# References
